title

### 2016-04-28 paper.tex
paper updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

In this section we examine the design space for mapping the CORFU protocol onto
the RADOS storage system. Recall from Section X the options for rados,
and from section Y for corfu options. The cross product forms the design space.
Want to winnow this down.

@@

@@

Constructing a complete implementation for each configuration would take
a lot of time, and may be time wasted if some configurations can be shown
to never be a viable option.

To winnow down the design space we ran a set of benchmarks---one for each
configuration--- that stressed the raw write performance using the built-in,
optimized interfaces on an unmodified version of Ceph. We explicitly avoided
simulating the costs associated with indexing or protocol enforcement in order
to form a clean baseline. Log entries may vary in size depending on the
application, but per-entry metadata is constant.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{experiments/librados-sweep/output.soft.reset.png}
  \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/librados-sweep/visualize.ipynb}{source}]
Throughput (IOPS) of 1K writes to a single OSD using the standard I/O
interfaces in various configurations. The best performance is achieved using
the byte stream interface and a N:1 mapping strategy.
}
\end{figure}

The first thing to notice is that the configurations using a 1:1 mapping
perform poorly relative to the other configurations. This is unfortunate
because a 1:1 mapping simplifies data management by avoiding the need to
multiplex entries onto a smaller set of objects. However, even if performance
was acceptable, notice that throughput dramatically drops in the tail when the
number of objects reaches a threshold forcing the object cache to spill to
disk. Note that in a large cluster this mode may take a long time reach,
but we avoid it due to the inherent risk.

The KV/N:1 is a convenient configuration because the key-value interface
can be used to easily address log entries and manage index data. However, the
performance of KV/N:1 can vary widely depending on the size of the data entry.
As we will see next, even though the KV/N:1 configuration simplifies data
management, small entry performance falls behind that of N:1 configurations
that store data in the stream interface.

@@

Figure \ref{f:librados-sweep} shows the single-node write-only I/O throughput
for each of the points in the design space defined in Table \ref{t:init-ds}.
The results reveal poor relative performance using both the key-value storage
interface, as well as either of the 1:1 strategies---which incur overhead by
creating a new object for each log entry. Both of the N:1 strategies using the
bytestream I/O interface outperform all of the other approaches by over 2x
throughput, but otherwise have nearly identical performance. As a first
approximation these results show that when optimizing for log append throughput
the design space should be refined by limiting solutions to architectures based
on a N:1 mapping strategy using the bytestream I/O interface.

The configurations based on bytestream storage exhibit the best performance.
The *write* variation depends on client-side mapping to object offset and
indirectly on the VFS index layer within the OSD, but this method is
incompatible with non-fixed size entries. Alternatively, the *append* variation
supports both fixed and dynamic size entries, but leaves the indexing and
protocl enforcment challenges unsolved.

In conclusion, both *write* and *append* variation of bytestream configurations
are the best choice, with an edge given to *append* if it can support dynamic
sized entries without sacrificing performance.

>>>>

In this section we examine the design space for implementing the CORFU
protocol in the RADOS storage system. Table \ref{t:init-ds} shows the entire
design space. A description of each design parameter follows:

{\bf Mapping strategy.} The method by which a log entry---identified by its
logical position---is addressed within RADOS is referred to as the mapping
strategy. A 1:1 strategy stores each log entry in a RADOS object with a
distinct name (e.g. ``mylog.pos443''), and an N:1 strategy stripes the log
positions across a set of objects (e.g.  round-robin). While we do consider
both strategies in this paper, a 1:1 strategy is attractive because it allows
a design in which clients can directly address log positions by constructing
the correct object name.

{\bf Storage interface.} entry data may be small or large. its primary
storage location is important. kv, bs. we further sub-divide bs into
write and append. each strategy is compatible with fixed size entries
except for the write interface.

{\bf Logical addressing.}

@@

Figure \ref{f:librados-sweep} shows the single-node write-only I/O throughput
for each of the points in the design space defined in Table \ref{t:init-ds}.
The results reveal poor relative performance using both the key-value storage
interface, as well as either of the 1:1 strategies---which incur overhead by
creating a new object for each log entry. Both of the N:1 strategies using the
bytestream I/O interface outperform all of the other approaches by over 2x
throughput, but otherwise have nearly identical performance.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{experiments/librados-sweep/output.soft.reset.2hr.png}
  \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/librados-sweep/visualize.ipynb}{source}]
Throughput (IOPS) of 1K writes to a single OSD using the standard I/O
interfaces in various configurations. The best performance is achieved using
the byte stream interface and a N:1 mapping strategy.
}
\end{figure}

@@

As a first approximation these results show that when optimizing for log
append and random read throughput the design space should be refined by
limiting solutions to architectures based on a N:1 mapping strategy using the
bytestream I/O interface. But what these microbenchmarks explicitly omit are
the overheads associated with metadata management such as enforcing write-once
semantics or using an index to map a log position to a physical offset within
an object. In the next section we
